---
title: "HW2-Min"
author: "Jie Min"
date: "9/10/2019"
output: pdf_document
---
## Problem 3

One way version control can help me is that wherever I am and whenever I want, I can review my previous codes. I can easily download my previous code and continue doing my work when I am outside home or school.

## Problem 4

**a**

First several rows of the cleaned data and the summarize of the cleaned data is showed below:

```{r}
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
data1<-read.table(url,header=FALSE,skip=2,fill=TRUE) 
data1<-cbind(data1,matrix(0,ncol=1,nrow=nrow(data1)))
idx<-seq(1,30,3)
data1[idx,2:7]<-data1[idx,1:6]
data1[-idx,3:7]<-data1[-idx,1:5]
data1<-data1[,-2]
data1[,1]<-sort(rep(1:10,3))
colnames(data1)<-c('Item','1','2','3','4','5')

```
```{r,echo=FALSE}
head(data1)
summary(data1[,-1])
```


The data is the observed value of 10 itmes on 5 operators, however in the raw data, not each row has the number of items, so some lines have 5 numbers and some lines have 6 numbers in the origin dataset.

I first filled the blank as NA when importing the data to make sure each row has same number of columns.Then I right align the dataframe, and filled the missed item number into the first column for lines that don't have this value.

The issue of the uncleaned data is that it has missing values in 'Item' column. I didn't see any issue in the cleaned data.

**b**

First several rows of the cleaned data and the summarize of the cleaned data is showed below:

```{r}
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat"
data1<-read.table(url,skip=1,fill=TRUE) 
data1<-as.matrix(cbind(data1,matrix(NA,ncol=1,nrow=nrow(data1))))
data2<-rbind(data1[,c(2,3)],data1[,c(4,5)],data1[,c(6,7)],data1[,c(8,9)])
data2<-as.data.frame(cbind(rep(data1[,1],4),data2))
colnames(data2)=c('Year','Long','Jump')
data2<-data2[order(data2$Year),]
data2[,1]<-data2[,1]+1990

```

```{r,echo=FALSE}
rownames(data2)<-NULL
head(data2)
summary(data2[,-1],na.rm=TRUE)
```

For this data, I gathered columns that are data from the same year into rows. Finally I have three columns in the cleaned data table, the first column is year, the second column is Long and the third column is Jump. 

The issue of this data is that it has several Na values. I didn't remove those Na's, but when calculating summary statistics, I omitted those Na's, and only used data we have.

**c**
```{r}
url<-'http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat'
data1<-as.matrix(unname(read.table(url,skip=1,fill=TRUE))) 
data1<-cbind(seq(1,21,1),data1)
data2<-rbind(data1[,c(2,3)],data1[,c(4,5)],data1[,c(6,7)])
data2<-as.data.frame(cbind(rep(seq(1,21,1),3),data2))
colnames(data2)<-c('N','BodyWt','BrainWt')
data2<-data2[order(data2$N),]
data2<-data2[-63,-1]
```
```{r,echo=FALSE}
rownames(data2)<-NULL
head(data2)
summary(data2)
```


For this data, I gathered columns that are data into rows.I have two columns in the cleaned data table, the first column is BodyWt, the second column is BrainWt.

There are several issues about this data. First, there is no value about which bodywt and brainwt are for which species. Second, the recorded value may have some problem. For example, for the value in the first row, bodywt is much more smaller than brainwt is not reasonable.


**d**

```{r}
url<-'http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat'


l<- readLines(url)[c(3,4)]
l<-gsub(" ",',',l)
data1<-as.matrix(read.table(text=l,comment.char = '*',sep=',',fill=TRUE)[,-1])
id1<-which(is.na(data1[1,])==TRUE)
id2<-which(is.na(data1[2,])==TRUE)
data2<-as.data.frame(rbind(data1[1,-id1],data1[2,-id2]))

```
```{r,echo=FALSE}
rownames(data2)<-c('Ife#1','PusaEarlyDwarf')
  colnames(data2)<-c(10000,10000,10000,20000,20000,20000,30000,30000,30000)
head(data2)
summary(data2)
```


When reading the table, I changed the separate character from "" to ",". Then after reading in the table, I removed all blank cells, and finally got a clean dataset with two rows and nine columns.

The issue of original data is that data are separated both by ',' and by blank, thus it is difficult to read into r. I didn't see any issue in the cleaned data.


## Problem 5
```{r,echo=FALSE,include=FALSE}
library(swirl)
.datapath <- file.path(path.package('swirl'), 'Courses',
                      'R_Programming_E', 'Looking_at_Data',
                      'plant-data.txt')
# Read in data
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")

# Remove annoying columns
.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]

# Make names pretty
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
                   'Foliage_Color', 'pH_Min', 'pH_Max',
                   'Precip_Min', 'Precip_Max',  'Shade_Tolerance', 'Temp_Min_F')
```

First, omit all rows that have NA values. Then we use the average value as a statistic that combines the information of pH_Min and pH_Max. A summary of the data is listed below.

```{r}
plants1<-na.omit(plants)
plants1$pH<-(plants1$pH_Max+plants1$pH_Min)/2
```

```{r,echo=FALSE}

head(plants1)
summary(plants1)
```

Then by lm, we tested the relationship between Foliage_Color and pH. The coefficients and ANOVA results are listed in tables below. We can see that Foliage_Color and pH have strong relationship.


```{r}
model1<-lm(pH~Foliage_Color,data=plants1)
model2<-anova(lm(pH~Foliage_Color,data=plants1))
```

```{r,echo=FALSE}
knitr::kable(model1$coefficients,caption='Coefficients')
knitr::kable(model2,caption='ANOVA TABLE')
```

