---
title: "Hw4"
author: "Jie Min"
date: "9/24/2019"
output: pdf_document
---

## Problem 4

After reading these two links I discovered a good coding style can help others quickly understand what I was doing, which is very important in teamwork. I will check my codes every time after coding and correct my bad coding style.  


## Problem 5
```{r eval=F, echo=T}
library(lintr)
lint(filename = "C:\\courses\\rpackage\\STAT_5014_2019_jiem\\HW3_Min.Rmd")
```

I need to change all single quotes to  double quotes, put space after commas, put spaces around infix operators, and use '<-' instead of '=' in coding. 

## Problem 6
```{r,echo=FALSE}
data <- readRDS("C:\\Users\\Jie Min\\Documents\\GitHub\\STAT_5014_Fall_2019\\homework\\HW4_data.rds")
```
```{r}
.summary_dev <- function(data){
  re <- NULL
  obs <- unique(data[, 1])
  for(i in 1:max(obs)){
  
  idx <- which(data[, 1]==i)
  n <- length(idx)
  mean1 <- mean(data[idx, 2])
  mean2 <- mean(data[idx, 3])
  sd1 <- sd(data[idx, 2])
  sd2 <- sd(data[idx, 2])
  corr <- cor(data[idx, 2],data[idx, 3])
  r <- cbind(i, mean1, mean2, sd1, sd2, corr)
  re <- rbind(re, r)
  
  }
  colnames(re) <- cbind(c("Observer", "dev1mean", "dev2mean", "dev1sd", "dev2sd", "correlation"))
  resut <- as.data.frame(re)
  return(resut)
  }
```
```{r,echo=FALSE}
library(ggplot2)
summ <- .summary_dev(data)
print(summ)

par(mfrow=c(1,2))
boxplot(summ[,2], ylab='dev1mean')
boxplot(summ[,3], ylab='dev2mean')

plot1 <- ggplot(summ, aes(x=Observer,y=dev1sd))+geom_violin(trim=FALSE)
plot2 <- ggplot(summ, aes(x=Observer,y=dev2sd))+geom_violin(trim=FALSE)
gridExtra::grid.arrange( plot1, plot2, ncol=2)
```


I created side-by-side box plots and violin plots because the absolute value of mean and sd are very different between dev1 and dev2 so if I put two box plots(violin plots) together with same ylim, each box would be too small.


## Problem 7

```{r}
.Reimann_int <- function(width){
    grid <- seq(0, 1, width)
    y <- exp(-(grid^2)/2)
    lefts <- sum(width*y[1:(length(y)-1)])
    rights <- sum(width*y[2:length(y)])
    re <- (lefts+rights)/2
    return(re) 
}

width <- c(0.5, 0.1, 0.05, 0.01, 0.005, 0.001)
re <- NULL
for(i in 1:length(width)){
  r <- .Reimann_int(width[i])
  re <- cbind(re, r)
}

true <- 0.855624
err <- 10^(-6)
er <- abs(true-re)
re <- rbind(re,er)
colnames(re) <- c('0.5', '0.1', '0.05', '0.01', '0.005', '0.001')
rownames(re) <- c('Sum', 'error')
print(re)
id <- width[which(er<=err)]
```

Among my choices, the width that small enough to obtain an answer within 1e^-6 of the analytic solution is 0.005 and 0.001.



## Problem 8


$f(x) = 3^x - sin(x) + cos(5x)$

$f'(x)=xlog3-cox(x)-5sin(5x)$

```{r}
.find_root <- function(x1, tolerance=10^(-5)){
  
  error <- 1
  xx <- x1
  while(error>=tolerance){
  x <- x1
  f <- 3^x-sin(x)+cos(5*x)
  fd <- x*log(3)-cos(x)-5*cos(5*x)
  x1 <- x-f/fd
  f1 <- 3^x1-sin(x1)+cos(5*x1)
  error <- abs(f1-0)
  xx <- c(xx,x1)  
  }
  
  return(xx)
}


fx <- .find_root(x1=-1)
```
```{r,echo=FALSE}
plot(fx,type='l', ylab='x-value')
final <- fx[length(fx)]
ma <- max(fx)
mi <- min(fx)
knitr::kable(cbind(final, '[-26.27,2.32]', 10^(-5)), col.names=c('final x value', 'x interval', 'tolerance'))
```

Starting from x=-1, with tolerance = 1e-5, the final x-value and interval is listed in the table above.


